TGI Spinal Analysis Code

### 2022-12-14 analysis/tgi-spinal_analysis.Rmd
running planned correlation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(boot, broom, broom.mixed, brms, caret, DHARMa, 
                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                 modelsummary, RColorBrewer, rcompanion, reshape2, Rmisc,
                 rsample, simr, tibble, tidyverse, wesanderson
                 )
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(boot, broom, broom.mixed, brms, caret, corrplot, DHARMa, 
                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                 modelsummary, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                 rsample, simr, tibble, tidyverse, wesanderson
                 )
```

@@

# EXPLORATORY HYPOTHESES
# Correlation between quality (cold/warm/burn)

```{r corr}
# remove columns
df_corr <- df_res[, c(1:9,14:16,21)]
df_corr <- df_corr %>% 
  pivot_wider(names_from = 'manipulation', values_from = c('VAScold','VASwarm','VASburn')) %>% 
  select(c(ID,VAScold_CNT,VAScold_TGI,VASwarm_CNT,VASwarm_TGI,VASburn_CNT,VASburn_TGI)) %>% 
  rename(NonTGI_cold = VAScold_CNT,
         TGI_cold = VAScold_TGI,
         NonTGI_warm = VASwarm_CNT,
         TGI_warm = VASwarm_TGI,
         NonTGI_burn = VASburn_CNT,
         TGI_burn = VASburn_TGI)

# average values within participants
df_corr <- aggregate(. ~ID, mean, data = df_corr)
# remove ID
df_corr <- select(df_corr, -ID)

# correlate
cormat <- hetcor(df_corr, type = 'pearson')$correlations
cormat

# significance values

# correlation matrix
# plotting correlations between variables
corrplot(cormat, method="circle", addrect = 0,
         title = "VAS rating correlation matrix", mar = c(0,0,1,0), 
         tl.cex=0.9) 
```
